---
title: "Simple document"
author: Arghya Kannadaguli
date: 2024-09-10
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

```{r echo = FALSE, message = FALSE}
library(tidyverse)
```

I loaded necessary packages (e.g. `tidyverse`).

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r echo = FALSE}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3: Learning Assessment

This is code for the learning assessment at P9105. It creates a dataframe `df` and then plots a histogram.

```{r message = FALSE}

df = tibble(
  vec_numeric = rnorm(500, mean = 1),
  vec_logical = (vec_numeric > 0),
  vec_abs = abs(vec_numeric)
)

plot_df = tibble(
  x = df$vec_abs
)

ggplot(plot_df, aes(x = x)) + geom_histogram()

```


The median value of this distribution is `r round(median(df$vec_numeric), digits = 2)`.



# Section 4: Rmd Formatting

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell





